Web Service Community \\ Learning

### 2014-06-05 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\IEEEPARstart{O}{ver} Introduction

>>>>

\IEEEPARstart{O}{ver} 
the past years, online services have become part of many scalable business applications. The increasing reliance on online service providers has significantly influended the way web services are engineered. Web services provide a set of stateless software functions accessible at a network address over the web.

- The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges. Delivering high quality services considering the dynamic and unpredictable nature of the Internet is still a very critical and challenging issue.

- High demand on online services has created a massive business competition. For example, nowadays users are provided with multiple choices of web services offering local places information such as coffees, venues, and shops nearby a geographic position. It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other available services, even if they provide a high quality of service. Hence, the concept of communities of web services provides them with the chance of joining a platform with an established market share and reputation. However, it is crucial
for a community manager to consider many factors when inviting or accepting new members. For example,  this may hurt the community stability.

- The high competition within the services industry requires applications to use reliable and high quality online service providers. If the user were to check a web site or run an application on her mobile device upon having downtime, or having high response delay or encountering any non-satisfying quality metric, she will instantly remove the application, which is a huge business concern for application providers. For example, if a user installs a ticketing application on her mobile device and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.

- Most applications cannot independently satisfy users requests and should rely on different online services. The high competition within the services industry requires applications to use reliable and high quality online service providers.

Today web services are

- softwares rely on third party online service providers 
- quality of services determines the success of the business 
- services want to maximise thier utility by cooperating with best possible communities
- services need to get visible and join market
